The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-04 papers/pair-correlation/paper.tex
fix offsets Tested on bennet. Took 0:45.50.

\newcommand\paircaption{The pair distribution function near a hard
  wall, with packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with
  the hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$
  as $\rr_2$ varies.  The top half of this figure shows the result of the
  Monte Carlo simulation, while the bottom half shows the result of
  the appproximation developed in this work.  On the right is a plot
  of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the figure to
  the left.  This plot compares the Monte Carlo results (black) with
  those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work} The triplet distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at
    packing fraction 0.3, plotted when $\rr_1$ and $\rr_2$ are in contact.  The
    color plot on the left shows the triplet distribution function, with white
    corresponding to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path shown as a
    dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}

@@

\begin{figure}
  \begin{subfigure}{0.5\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{0.5\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{0.5\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard wall.  (a) shows a
    sticky hard-sphere fluid defined by a pair potential
    $\delta(\sigma-r+\delta)$ where $\sigma$ is the hard-sphere
    diameter, and $\delta$ is an infinitesimal distance; (b) shows a
    square well fluid defined by a pair potential $\Theta(1.79
    \sigma-r)$; and (c) shows a hard-core inverse-sixth potential
    fluid with an attractive pair potential proportional to $r^{-6}$.
  }
  \label{fig:dadz}
\end{figure}

>>>>

\newcommand\paircaption{\fixme{Look into smoothing the top plot on
    right.} The pair distribution function near a hard wall, with
  packing fractions of 0.1 and 0.3 and $\rr_1$ in contact with the
  hard wall.  On the left is a 2D plot of $g^{(2)}(\rr_1,\rr_2)$ as
  $\rr_2$ varies.  The top half of this figure shows the result of the
  Monte Carlo simulation, while the bottom half shows the result of
  the appproximation developed in this work.  On the right is a plot
  of $g^{(2)}(\rr_1,\rr_2)$ on the path illustrated in the figure to
  the left.  This plot compares the Monte Carlo results (black) with
  those of this work (blue), Sokolowski and Fischer
  (red)~\cite{sokolowski1992role}, and Fischer and Methfessel
  (green)~\cite{fischer1980born}.  The latter is only plotted at
  contact, where it is defined.  }

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for
      this work}\fixme{Fix MC issue here (volume wrong?)} The triplet
    distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing
    fraction 0.3, plotted when $\rr_1$ and $\rr_2$ are in contact.
    The color plot on the left shows the triplet distribution
    function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows
    the value of $g^{(3)}$ along the path shown as a dotted line on
    the plot to the left.}\label{fig:triplet-contact-distribution}
\end{figure*}

@@

\begin{figure}
  \begin{subfigure}{1.0\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{1.0\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{1.0\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard wall.  (a) shows a
    sticky hard-sphere fluid defined by a pair potential
    $\delta(\sigma-r+\delta)$ where $\sigma$ is the hard-sphere
    diameter, and $\delta$ is an infinitesimal distance; (b) shows a
    square well fluid defined by a pair potential $\Theta(1.79
    \sigma-r)$; and (c) shows a hard-core inverse-sixth potential
    fluid with an attractive pair potential proportional to $r^{-6}$.
  }
  \label{fig:dadz}
\end{figure}
